Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring

### 2014-05-30 evaluation.tex
Revise evaluation section.

We implemented our monitoring architecture for adjustable overheads by
modifying the ARM version of the gem5 simulator \cite{gem5} to support parallel
run-time monitoring. In order to explore the generality of the architecture for
different monitors, we implemented three different monitors: uninitialized
memory check (UMC), array bounds check (BC), and dynamic information flow
tracking (DIFT).  Uninitialized memory check seeks to detect loading from
memory locations that are not initialized first.  Array bounds check, as
mentioned in Section~\ref{sec:monitoring} is a monitoring scheme that aims to
detect buffer overflows where memory accesses go beyond the boundaries of an
array.  Dynamic information flow tracking is a security monitoring scheme,
which detects when information from untrusted sources is used to affect the
program control flow.  We tested our system using 12 benchmarks from SPEC
CPU2006 \cite{spec2006}. For each benchmark, we simulated for 200 million
instructions. An initial slack of 2 million cycles, which is less than 1\% of
the total execution time, is given for a 10\% target overhead. This initial
slack is scaled proportionally for other overhead targets.

@@

Figure~\ref{fig:optimizations.full_mon} showed the execution time of benchmarks
with monitoring normalized to without monitoring. In this case, filtering was
not performed. UMC showed an 8x increase in execution
time on average while BC and DIFT showed average execution time increases of
21x and 14x respectively. Figure~\ref{fig:evaluation.filtering} shows the
normalized execution times with filtering enabled. We see significant
reductions in overhead for all three monitoring schemes. UMC sees normalized
execution times of 4x on average with filtering. For BC, normalized execution
times drop from 21x down to 3x. This is not surprising since in the baseline
implementation all loads and stores needed to be monitored. However, with
filtering, only loads and stores corresponding to arrays need to be forwarded.
Finally, DIFT sees the largest reduction in overheads with only 13\% overheads
on average. This is due to the fact that for our implementation of DIFT on SPEC
benchmarks, we mark data read from files as tainted. For most of these
benchmarks, this propagates to relatively few instructions. Instead, if we
targeted network or streaming applications we would expect to see a less
filtering

>>>>

We implemented our monitoring architecture for adjustable overheads by
modifying the ARM version of the gem5 simulator \cite{gem5} to support parallel
run-time monitoring. We model the main and monitoring cores as running at 2.5
GHz with 4-way set-associative private L1 I/D caches and a shared 8-way 2 MB L2
cache. This setup is similar to the Snapdragon 801 processor commonly found in
mobile systems. The dataflow engine uses a 1 kB cache for flags.

In order to explore the generality of the architecture for
different monitors, we implemented three different monitors: uninitialized
memory check (UMC), array bounds check (BC), and dynamic information flow
tracking (DIFT).  Uninitialized memory check seeks to detect loading from
memory locations that are not initialized first.  Array bounds check, as
mentioned in Section~\ref{sec:monitoring} is a monitoring scheme that aims to
detect buffer overflows where memory accesses go beyond the boundaries of an
array. We modify the implementation of {\tt malloc} to set base and bound
metadata information. Dynamic information flow tracking is a security
monitoring scheme,
which detects when information from untrusted sources is used to affect the
program control flow. For our DIFT implementation, we set mark data read from
files as untrusted. This data is marked with a 32-bit metadata identifier so
that if an error is detected, it is possible to have information about where
the information originated from.

We tested our system using all C benchmarks from SPECint
CPU2006 \cite{spec2006}. We focus on the C benchmarks because of our
modification of {\tt malloc} to support array bounds check. Although we do not
show results for the C++ benchmarks, we note that the results for UMC and DIFT
for these benchmarks are similar to the other results shown. For each
benchmark, we simulated for 200 million
instructions. An initial slack of 2 million cycles, which is less than 1\% of
the total execution time, is given for a 10\% target overhead. This initial
slack is scaled proportionally for other overhead targets.

\subsection{Baseline Monitoring Overheads}
% Full monitoring overheads
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/data_full_mon.pdf}
    \vspace{-0.2in}
    \caption{Full monitoring overheads for UMC, BC, and DIFT.}
    \label{fig:evaluation.full_mon}
    \vspace{-0.1in}
  \end{center}
\end{figure} Figure~\ref{fig:evaluation.full_mon} shows the execution times of
performing full monitoring normalized to the execution times of the benchmarks
without monitoring. In these results, no filtering or partial monitoring is
done. UMC shows normalized execution times from 5x to 11x with an average
of 8x. BC shows normalized execution times of 15-28x with an average of
22x while DIFT shows normalized execution times of 11x-17x with an average of
14x. One of the reasons for these high overheads is that our implementations of
these monitors dynamically allocate memory for new metadata. This can be an
expensive, multi-cycle operation. Statically allocating memory for metadata
will reduce the execution time but requires a large upfront memory footprint.

@@

Figure~\ref{fig:evaluation.filtering} shows the
normalized execution times with filtering enabled. We see significant
reductions in overhead for all three monitoring schemes. UMC sees normalized
execution times of 4x on average with filtering. For BC, normalized execution
times drop from 21x down to 3x. This is not surprising since in the baseline
implementation all loads and stores needed to be monitored. However, with
filtering, only loads and stores corresponding to arrays need to be forwarded.
Finally, DIFT sees the largest reduction in overheads with only 13\% overheads
on average. This is due to the fact that for our implementation of DIFT on SPEC
benchmarks, we mark data read from files as tainted. For most of these
benchmarks, this propagates to relatively few instructions. Instead, if we
targeted network or streaming applications we would expect to see a less
filtering
